Bootstrapping Multi-atlas Hippocampal Segmentation with \mb

### 2013-08-21 paper.Rnw
A few tense changes

In this experiment, our dataset consists of 69 1.5T images and corresponding \gs
segmentations. In each validation round, the dataset is partitioned into a
training set consisting of images and their \gs segmentations to be used as an
atlas library, and a validation set consisting of the remaining images segmented
by both \mb and multi-atlas. The computed segmentations are compared to the
\gs segmentations (see below).

A total of ten validation rounds are performed on each subject in the dataset,
over each combination of parameter settings. The parameter settings
we explore are: atlas library size (1-9), template library size (1-20),
registration method (\ants or \animal), and label fusion method (majority vote,
cross-correlation weighted majority vote, and normalized mutual information
weighted majority vote).  A total of $10 \times 69 \times 9 \times 20 \times 2
\times 3 = \num{7452000}$ validation rounds were conducted, resulting in a total
of $\num{1490400}$ segmentations analysed.

@@

To validate the \mb algorithm with respect to other established automated
methods, \mb is applied to large dataset from the ADNI project and the
resulting segmentations are compared to those produced by FreeSurfer, FSL,
MAPER and by expert semi-automated manual segmentations (SNT).

\paragraph{ADNI1 dataset revisited} 
The $1919$ images from the {\em \adnidataset} standardized dataset, described
in Experiment 1, were initially considered.  SNT and FreeSurfer hippocampal
volumes were provided by ADNI, along with FreeSurfer quality control data
(guidelines described in \citep{Hartig2010}). Clinical and demographic data for
the entire \adnidataset dataset are shown in Table
\ref{tab:ADNI1-Dataset-Demographics}.

\paragraph{Experiment details} 
\mb was configured with an atlas library composed of the five Winterburn T1
atlases (described in Experiment 2). The optimal size of template library,
registration method, and label fusion method found in Experiment 1 were used.
The FSL FIRST segmentation method was used  via the \verb+run_first_all+ script
according to the FIRST user guide
\footnote{http://fsl.fmrib.ox.ac.uk/fsl/fslwiki/FIRST/UserGuide}.  All images
from the \adnidataset dataset were segmented by both methods.

>>>>

In this experiment, our dataset consists of 69 1.5T images and corresponding \gs
segmentations. In each validation round, the dataset is partitioned into a
training set consisting of images and their \gs segmentations to be used as an
atlas library, and a validation set consisting of the remaining images segmented
by both \mb and multi-atlas. The computed segmentations were compared to the
\gs segmentations (see below).

A total of ten validation rounds were performed on each subject in the dataset,
over each combination of parameter settings. The parameter settings
explored are: atlas library size (1-9), template library size (1-20),
registration method (\ants or \animal), and label fusion method (majority vote,
cross-correlation weighted majority vote, and normalized mutual information
weighted majority vote).  A total of $10 \times 69 \times 9 \times 20 \times 2
\times 3 = \num{7452000}$ validation rounds were conducted, resulting in a total
of $\num{1490400}$ segmentations analysed.

@@

To validate \mb segmentation quality with respect to other established automated
methods, \mb is applied to large dataset from the ADNI project and the resulting
segmentations are compared to those produced by FreeSurfer, FSL, MAPER and by
expert semi-automated manual segmentations (SNT).

\paragraph{ADNI1 dataset revisited} 
The {\em \adnidataset} standardized dataset contains $1919$ images in total.
SNT and FreeSurfer hippocampal volumes for a subset of images are provided by
ADNI, along with quality control data for each FreeSurfer segmentation
(guidelines described in \citep{Hartig2010}).  Clinical and demographic data for
the entire \adnidataset dataset are shown in Table
\ref{tab:ADNI1-Dataset-Demographics}.

\paragraph{Experiment details} 
\mb was configured with an atlas library composed of the five Winterburn T1
atlases (described in Experiment 2), and the size of template library,
registration method, and label fusion method found in Experiment 1 were used.
The FSL FIRST segmentation method was used via the \verb+run_first_all+ script
according to the FIRST user guide
\footnote{http://fsl.fmrib.ox.ac.uk/fsl/fslwiki/FIRST/UserGuide}.  All images in
the \adnidataset dataset were segmented by both methods.
